Concurrent Programming with CXL

### 2020-05-21 book/paper.tex
Latest

Because each \texttt{private[i]} is only access by process~$i$,
there is no need to keep \texttt{private} as a shared
variable---we only did so to be able to show and check the invariants.
Figure~\ref{fig:tas2} shows a more straightforward implementation.
Compared to Peterson's Algorithm, this approach is general for
any number of processes.

@@

Like in Python, CXL methods have local variables.  You have already
seen two types of local variables.
First, the arguments to the method are variables, although read-only.
Second, the variable \texttt{result} can be assigned to
change the default return value of a method, which is \texttt{()}.
You can declare additional local variables to hold intermediate
results.  For example, you can
declare a local variable $x$ with initial value 3 as follows:
\begin{code}
\begin{verbatim}
var x = 3;
\end{verbatim}
\end{code}
The initial value is mandatory.
Unless a variable is declared this way, it will be considered
a global shared variable.
The local variables of a method cannot be accessed other than by
the method itself.

>>>>

In Figure~\ref{fig:tas} we have shown a solution based on a shared
variable and a private variable for each process.   The private
variables themselves are implemented as shared variables as well,
but they are accessed only by their respective processes.
There is no need to keep \texttt{private} as a shared
variable---we only did so to be able to show and check the invariants.
Figure~\ref{fig:tas2} shows a more straightforward implementation.
The solution is similar to the na\"{i}ve solution of Figure~\ref{fig:uplock},
but uses test-and-set to check and set the lock variable atomically.
Compared to Peterson's Algorithm, this approach is general for
any number of processes.

@@
